Supplementary Material for Asymmetry paper

### 2020-05-14 Supplementary/Sup_mat.Rmd
updated supmat

The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\phi\approx0.5$, in this case 0.5 is considered the central point with 0 and 1 representing the left and right hoop respectively. We assumed that by introducing a difference in size between the two hoops that this distribution would shift towards the smaller hoop so as to balance their chances of success. We assumed that the difference in hoop size would cause particiapnts to stand slightly closer to the small hoop, in this case the shift in mean would be +0.05. 
```{r Hoop Size resampling, include = T, echo = F}
# setup loop
n_iter <- 5000
n_subs <- seq(3, 24, 1)
n_trials <- 72

@@

# load data
load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")

@@

>>>>

The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\phi\approx0.5$, in this case 0.5 is considered the central point with 0 and 1 representing the left and right hoop respectively. We assumed that by introducing a difference in size between the two hoops that this distribution would shift towards the smaller hoop so as to balance their chances of success. We assumed that the difference in hoop size would cause particiapnts to stand slightly closer to the small hoop, in this case the shift in mean would be +0.05. 
```{r Hoop Size resampling, include = T, echo = F, cache = T}
# setup loop
n_iter <- 5000
n_subs <- seq(3, 24, 1)
n_trials <- 72

@@

# load data
# load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")

@@

``` {r two-throw power, include = F, echo = F, cache = T}
# setup loop parameters
n_iter <- 5000
n_subs <- seq(2, 28, 2) 
n_trials <- c(12, 60)
dists <- c("90%", "10%")

# setup data 
n <- n_iter * length(n_subs) * length(n_trials) * length(dists)

df_sample <- data.table::data.table(iter = rep(0, n),
                                    n_subs = rep(0, n),
                                    n_trials = rep(0, n),
                                    dist_type = rep("", n),
                                    baseline = rep(0, n),
                                    comparison = rep(0, n))
# 
# # TODO make this loop quicker by using data.table()
# # split dataset for ease of access...
df_Av <- df_all %>%
  filter(condition == "Avatar")
df_Th <- df_all %>%
  filter(condition == "Throwing")

# start counter
count <- 0
# loop through
for(ii in 1:n_iter){
  # loop distances
  for(dist in dists){
    base_ss <- df_Th %>%
      filter(standard_lab == dist)
    comp_ss <- df_Av %>%
      filter(standard_lab == dist)
    for(trials in n_trials){
      for(subs in n_subs){
        # get random subjects
        base_subs <- sample(df_Th$participant, subs, replace = T)
        comp_subs <- sample(df_Av$participant, subs, replace = T)

        # loop through subjects
        base_sample <- c()
        comp_sample <- c()
        for(sub in 1:subs){
          base_temp <- base_ss %>%
            filter(participant == base_subs[sub])
          comp_temp <- comp_ss %>%
            filter(participant == comp_subs[sub])
          base_sample <- c(base_sample,
                           sample(base_temp$norm_pos, trials, replace = T))
          comp_sample <- c(comp_sample,
                           sample(comp_temp$norm_pos, trials, replace = T))
          if(sub == subs){
            count <- count + 1
            # input into table
            df_sample[count, iter := ii]
            df_sample[count, n_subs := subs]
            df_sample[count, n_trials := trials]
            df_sample[count, dist_type := dist]
            df_sample[count, baseline := mean(base_sample)]
            df_sample[count, comparison := mean(comp_sample)]
          }
        }
      }
    }
  }
}
